oREV item selection

### 2022-11-08 analysis/item_selection.Rmd

```{r}
frq_sel_items <- item_sel%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  arrange(-n)%>%
  slice(1:20)%>%
  pull(targetWord)

@@

```{r, message=F, warning=F, comment=F}
sim_rasch <- simulated_annealing_rasch(20)

@@

   sim <- simulated_annealing(25)

@@

frq_sel_items_rasch <- item_sel_rasch%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  arrange(-n)%>%
  slice(1:20)%>%
  pull(targetWord)

@@

```{r}
rasch_fit%>%
  filter(targetWord %in% frq_sel_items_rasch)%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index))+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,3)+
  theme_bw()
```

@@

```{r}
icc1_sel <- posterior_samples(irt1)%>% 
  select(b_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord"), names_to = "item", values_to = "xi") %>%
  mutate(item = str_extract(string = item, pattern = "(?<=\\[).*(?=,Intercept\\])"))%>%
  filter(item %in% sel_items_rasch)%>%
  expand(nesting(iter, b_Intercept, item, xi),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  mutate(p = inv_logit_scaled(b_Intercept + xi + theta)) %>% 
  group_by(theta, item) %>% 
  summarise(p = mean(p))%>%
  left_join(aoa%>%rename(item = targetWord))
```

```{r}
icc1_sel %>% 
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  geom_line() +
  #facet_wrap(~group)+
  #guides(col = F)+
  scale_color_viridis_c(name = "AoA") +
  labs(title = "ICCs for the 1PL",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  theme_minimal()
```

>>>>

```{r}
frq_sel_items <- item_sel%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  arrange(-n)%>%
  slice(1:22)%>%
  pull(targetWord)

@@

```{r, message=F, warning=F, comment=F}
sim_rasch <- simulated_annealing_rasch(22)

@@

for (i in 1:20) {

   sim <- simulated_annealing(22)

@@

frq_sel_items_rasch <- item_sel_rasch%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  arrange(-n)%>%
  slice(1:22)%>%
  pull(targetWord)

@@

```{r}
rasch_fit%>%
  filter(targetWord %in% frq_sel_items_rasch)%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index))+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge(width = 0.5))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,3)+
  theme_bw()
```

@@

```{r}
icc1_sel <- posterior_samples(irt1_guess)%>% 
  select(b_eta_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord"), names_to = "item", values_to = "xi") %>%
  mutate(item = str_extract(string = item, pattern = "(?<=\\[).*(?=,Intercept\\])"))%>%
  filter(item %in% sel_items_rasch)%>%
  expand(nesting(iter, b_eta_Intercept, item, xi),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  mutate(p = 0.25 + 0.75*inv_logit_scaled((b_eta_Intercept + theta + xi))) %>%  
  group_by(theta, item) %>% 
  summarise(p = mean(p))%>%
  left_join(aoa%>%rename(item = targetWord))
```

```{r}
icc1_sel %>% 
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  geom_line() +
  #facet_wrap(~group)+
  #guides(col = F)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  scale_color_viridis_c(name = "AoA") +
  labs(title = "ICCs for the 1PL",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```
